The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Added note indicating paper will need to change depending on how guessFPT changes

            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval .  A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number. If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.

>>>>

            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval .  A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number. {\color{red} This will need to get updated} If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
